A More Complete Algebra for File Synchronization

### 2015-11-08 2015/paper.tex
Same-pairs do not commute

\begin{description}
\item[Unrelated.] If the two paths in the pair are not directly related, then
the commands commute with an equivalence and they will not break every filesystem:
\begin{align*}
[\cxy(p,V_Y); \czw(\np,V_W)] &\equiv [\czw(\np,V_W); \cxy(p,V_Y)] \\
&\nequiv \cbrk
\end{align*}
%
\item[Same.] If the two paths are the same ($[\cxy(p,V_Y); \czw(p,V_W)]$), then:
\begin{description}
\item[Break.]
The pair will break every filesystem if $Z\ne Y$, that is, if the second
command expects a type of value different from the one left by the first command.
\item[Simplified by extension.]
Otherwise, the pair will simplify to a single or no commands
if both $X$ and $W$ are $\fsregcommandchar{\empt}$ or $\fsregcommandchar{D}$:
\begin{gather*}
% bf=fb Sp
           [\cbf(p, F); \cfb(p)] \eqext \emptyseq \\
% bd=db Sp
           [\cbd(p, D); \cdb(p)] \eqext \emptyseq \\
% db=bd Sp
           [\cdb(p); \cbd(p, D)] \eqext [\cdd(p, D)] \\
% df=fd Sp
           [\cdf(p, F); \cfd(p, D)] \eqext [\cdd(p, D)]
\end{gather*}
\item[Simplified by equivalence.]
In all other cases, the commands are equivalent to a single command
replacing the input of the first command with the output of the second:
\[ [\cxy(p, V_Y); \cyz(p, V_Z)] \equiv [\cxz(p, V_Z)] \]
\end{description}
%
\item[Down.]
These are the pairs in which the first command is applied to the parent of the path
of the second command.
\begin{description}
\item[Construction.] There are pairs in this group to which no law applies.
We call these ``construction'' pairs:
\begin{gather*}
% bd>bf
           [\cbd(\pp, D); \cbf(p, F)] \\
% bd>bd
           [\cbd(\pp, D_1); \cbd(p, D_2)] \\
% fd>bf
           [\cfd(\pp, D); \cbf(p, F)] \\
% fd>bd
           [\cfd(\pp, D_1); \cbd(p, D_2)]
\end{gather*}
\item[Commute.] Otherwise, the commands in these pairs commute iff the first command is $\cdd$. For example:
\begin{gather*}
[\cdd(\pp, D); \cbf(p, F)] \equiv [\cbf(p, F); \cdd(\pp, D)]
\end{gather*}
\item[Break.] All other pairs break every filesystem, e.g.:
\begin{gather*}
[\cdf(\pp, F); \cbd(p, D)] \equiv \cbrk
\end{gather*}
\end{description}
%
\item[Up.]
The final group of pairs are the ones in which the path in the second
command is the parent of the one in the first.
These behave similarly to the previous group. 
\begin{description}
\item[Desctruction.] There are
so-called ``destruction'' pairs to which no law applies:
\begin{gather*}
% fb<db ??
           [\cfb(p); \cdb(\pp)] \\
% fb<df ??
           [\cfb(p); \cdf(\pp, F)] \\
% db<db ??
           [\cdb(p); \cdb(\pp)] \\
% db<df ??
           [\cdb(p); \cdf(\pp, F)]
\end{gather*}
\item[Commute.] Otherwise the commands commute iff the \emph{second} command is $\cdd$.
\item[Break.] All other pairs break every filesystem.
\end{description}
\end{description}

@@

In real-life applications, we often do not want to consider metadata stored in
directories (\cite{BZ}). In other words, the contents of directories are all equal,
which can be modelled by assuming that $|\setd|=1$.
Note that this creates a convenient symmetry where there are only a single value
for each type, $D$ and $\empt$, that can be repeated as we move from a path to its child.

@@

\begin{description}
\item[Unrelated.] Pairs with unrelated paths are still reversible and not equivalent to
$\cbrk$, but these are the only pairs that are reversible.
%
\item[Same.] If the two paths are the same ($[\cxy(p,V_Y); \czw(p,V_W)]$), then:
\begin{description}
\item[Break.] As above, the pair will break every filesystem if $Z\ne Y$.
\item[Simplified by extension.] Otherwise, the pair is extended by an empty sequence
if both $X$ and $W$ are $\fsregcommandchar{\empt}$ or $\fsregcommandchar{D}$:
\begin{gather*}
% bf=fb Sp
           [\cbf(p, F); \cfb(p)] \eqext \emptyseq \\
% bd=db Sp
           [\cbd(p, D); \cdb(p)] \eqext \emptyseq \\
% db=bd Sp
           [\cdb(p); \cbd(p, D)] \eqext \emptyseq \\
% df=fd Sp
           [\cdf(p, F); \cfd(p, D)] \eqext \emptyseq
\end{gather*}
\item[Simplified by equivalence.]
And in all other cases, as above, the commands are equivalent to a single command
replacing the input of the first command with the output of the second:
\[ [\cxy(p, V_Y); \cyz(p, V_Z)] \equiv [\cxz(p, V_Z)] \]
\end{description}
%
\item[Down.]
Of the pairs in which the first command is applied to the parent path:
\begin{description}
\item[Construction.] the same ``construction'' pairs still have no laws, 
\item[Break.] but all other pairs break all filesystems.
\end{description}
%
\item[iv.]
And of the pairs where the second command
is applied to the parent path,
\begin{description}
\item[Destruction.] we still have the ``destruction'' pairs,
\item[Break.] and all other pairs break all filesystems.
\end{description}
\end{description}

>>>>

\begin{description}
\item[Unrelated.] If the two paths in the pair are not directly related, then
the commands commute with an equivalence and they will not break every filesystem:
\begin{align*}
[\cxy(p,V_Y); \czw(\np,V_W)] &\equiv [\czw(\np,V_W); \cxy(p,V_Y)] \\
&\nequiv \cbrk
\end{align*}
%
\item[Same.] If the two paths are the same ($[\cxy(p,V_Y); \czw(p,V_W)]$), the
the commands cannot be reversed. Instead:
   \begin{description}
   \item[Break.]
   The pair will break every filesystem if $Z\ne Y$, that is, if the second
   command expects a type of value different from the one left by the first command.
   \item[Simplified by extension.]
   Otherwise, the pair will simplify to a single or no commands
   if both $X$ and $W$ are $\fsregcommandchar{\empt}$ or $\fsregcommandchar{D}$:
   \begin{gather*}
   % bf=fb Sp
            [\cbf(p, F); \cfb(p)] \eqext \emptyseq \\
   % bd=db Sp
            [\cbd(p, D); \cdb(p)] \eqext \emptyseq \\
   % db=bd Sp
            [\cdb(p); \cbd(p, D)] \eqext [\cdd(p, D)] \\
   % df=fd Sp
            [\cdf(p, F); \cfd(p, D)] \eqext [\cdd(p, D)]
   \end{gather*}
   \item[Simplified by equivalence.]
   In all other cases, the commands are equivalent to a single command
   replacing the input of the first command with the output of the second:
   \[ [\cxy(p, V_Y); \cyz(p, V_Z)] \equiv [\cxz(p, V_Z)] \]
   \end{description}
%
\item[Down.]
These are the pairs in which the first command is applied to the parent of the path
of the second command.
   \begin{description}
   \item[Construction.] There are pairs in this group to which no law applies.
   We call these ``construction'' pairs:
   \begin{gather*}
   % bd>bf
            [\cbd(\pp, D); \cbf(p, F)] \\
   % bd>bd
            [\cbd(\pp, D_1); \cbd(p, D_2)] \\
   % fd>bf
            [\cfd(\pp, D); \cbf(p, F)] \\
   % fd>bd
            [\cfd(\pp, D_1); \cbd(p, D_2)]
   \end{gather*}
   \item[Commute.] Otherwise, the commands in these pairs commute iff the first command is $\cdd$. For example:
   \begin{gather*}
   [\cdd(\pp, D); \cbf(p, F)] \equiv [\cbf(p, F); \cdd(\pp, D)]
   \end{gather*}
   \item[Break.] All other pairs break every filesystem, e.g.:
   \begin{gather*}
   [\cdf(\pp, F); \cbd(p, D)] \equiv \cbrk
   \end{gather*}
   \end{description}
%
\item[Up.]
The final group of pairs are the ones in which the path in the second
command is the parent of the one in the first.
These behave similarly to the previous group. 
   \begin{description}
   \item[Desctruction.] There are
   so-called ``destruction'' pairs to which no law applies:
   \begin{gather*}
   % fb<db ??
            [\cfb(p); \cdb(\pp)] \\
   % fb<df ??
            [\cfb(p); \cdf(\pp, F)] \\
   % db<db ??
            [\cdb(p); \cdb(\pp)] \\
   % db<df ??
            [\cdb(p); \cdf(\pp, F)]
   \end{gather*}
   \item[Commute.] Otherwise the commands commute iff the \emph{second} command is $\cdd$.
   \item[Break.] All other pairs break every filesystem.
   \end{description}
\end{description}

@@

In real-life applications, we often do not want to consider metadata stored in
directories (\cite{BZ}). In other words, the contents of directories are all equal,
which can be modelled by assuming that $|\setd|=1$.
Note that this creates a convenient symmetry where there are only a single value
for each type that can be repeated as we move from a path to its child ($D$ and $\empt$).

@@

\begin{description}
\item[Unrelated.] Pairs with unrelated paths are still reversible and not equivalent to
$\cbrk$, but these are the only pairs that are reversible.
%
\item[Same.] If the two paths are the same ($[\cxy(p,V_Y); \czw(p,V_W)]$), then,
as above, the commands do not commute.
   \begin{description}
   \item[Break.] Also, as above, the pair will break every filesystem if $Z\ne Y$.
   \item[Simplified by extension.] Otherwise, the pair is extended by an empty sequence
   if both $X$ and $W$ are $\fsregcommandchar{\empt}$ or $\fsregcommandchar{D}$:
   \begin{gather*}
   % bf=fb Sp
            [\cbf(p, F); \cfb(p)] \eqext \emptyseq \\
   % bd=db Sp
            [\cbd(p, D); \cdb(p)] \eqext \emptyseq \\
   % db=bd Sp
            [\cdb(p); \cbd(p, D)] \eqext \emptyseq \\
   % df=fd Sp
            [\cdf(p, F); \cfd(p, D)] \eqext \emptyseq
   \end{gather*}
   \item[Simplified by equivalence.]
   And in all other cases, as above, the commands are equivalent to a single command
   replacing the input of the first command with the output of the second:
   \[ [\cxy(p, V_Y); \cyz(p, V_Z)] \equiv [\cxz(p, V_Z)] \]
   \end{description}
%
\item[Down.]
Of the pairs in which the first command is applied to the parent path:
   \begin{description}
   \item[Construction.] the same ``construction'' pairs still have no laws, 
   \item[Break.] but all other pairs break all filesystems.
   \end{description}
%
\item[Up.]
And of the pairs where the second command
is applied to the parent path,
   \begin{description}
   \item[Destruction.] we still have the ``destruction'' pairs,
   \item[Break.] and all other pairs break all filesystems.
   \end{description}
\end{description}
